% Copyright 2019 Matthew Felix Yuan
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
% 
% The Current Maintainer of this work is Matthew Felix Yuan.
%
% This work consists of the files blank-template.tex and sample-resume.tex.



\documentclass[11pt]{article}
% helpful packages.
\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{enumitem}
% global formatting tweaks.
\pagestyle{empty}
\geometry{margin=0.5in}
\setlength\parindent{9pt}
\setlist{nosep}
\renewcommand\labelitemi{--}
% new commands!
\newcommand{\name}[1]{\begin{center}\section*{\huge #1}\end{center}}
\newcommand{\topinfo}[1]{\begin{center}\vspace{-0.2cm}#1\vspace{-0.2cm}\end{center}}
\newcommand{\resumesection}[1]{\vspace{-0.2cm}\section*{#1}\vspace{-0.2cm}\hrule\vspace{0.2cm}}


\begin{document}

% \name is self-explanatory. \topinfo is for things like social media, email, phone number, address, etc.
\name{Ian Wesley Armstrong}
\topinfo{www.linkedin.com/in/ianwesleyarmstrong}
%\topinfo{www.github.com/ianwesleyarmstrong}
\topinfo{ianwesleyarmstrong@gmail.com}
\topinfo{(913) 908-2249}

% name your resume sections whatever you want!
\resumesection{Education}
% things written after \hfill will be right-aligned, which is where i usually put dates.
\textbf{Kansas State University} \hfill Manhattan, Kansas \hfill Expected May 2021  

% each \item is a point you want to say about the thing.
\textit{Bachelor of Science in Computer Science and Applied Mathematics}
\begin{itemize}
	\item 3.56 GPA
\end{itemize}

% fill your sections with things!
\textbf{Czech Technical University} \hfill Prague, Czechia \hfill January 2019 - May 2019 

\textit{Bachelor of Science in Information Technology }
\begin{itemize}
	\item Relevant Coursework: Data Mining, Introduction to Artificial Intelligence, Database Systems
\end{itemize}

% fill your resume with sections!
\resumesection{Experience}
\textbf{Commerce Bancshares}\hfill{IT Intern (DevOps/ETL)}\hfill{June - Present} 

\textit{Enterprise Data Warehousing}
\begin{itemize}
	\item Automated build of containerized Data Science environments using Puppet, Kubernetes and Docker.
	\item Environments are built on top of Red Hat Enterprise Linux, using Anaconda to manage Python/R packages with database connectivity to Teradata, SQL Server, S3 and Hive.
	\item Implemented a job scheduler using Airflow, enabling Data Scientists to develop workflow graphs and create robust pipelines for implementing models into production.
\end{itemize}

\textbf{Kansas State University}\hfill{Undergraduate Research Assistant}\hfill{January 2018 - February 2019} 

\textit{Johnson Cancer Research Center}
\begin{itemize}
	\item Contributed to the development of ORGANIC, a Python/Tensorflow framework to generate novel molecules. 
	\item ORGANIC uses Neural Networks and Reinforcement Learning to generate molecules with desired physical/chemical properties.
	\item Decreased runtime of ORGANIC by 30\% on our HPC cluster by modifying the molecular encoding system, allowing for quicker development and testing cycles.
\end{itemize}

\resumesection{Projects}
\textbf{Financial Data Warehouse}
\begin{itemize}
	\item Created a data warehouse for storing tick data about various financial instruments, including hourly Forex exchange rates and securities present in major indexes.
	\item Infrastructure is managed by Kubernetes, with Airflow being used to schedule all ETL processes.
	\item Time-series data is stored in TimescaleDB, while unstructured data is stored in HDFS.
\end{itemize}

\textbf{MLB Player Trade Evaluation}
\begin{itemize}
	\item Python Program that uses Logistic Regression to determine if a player is likely to be traded based on their historical offensive/defensive statistics, salary, and remaining length of contract.
\end{itemize}


% \textbf{Ant Colony Optimization}
% \begin{itemize}
% 	\item Implemented an Ant Colony Optimization heuristic in Python to solve the Travelling Salesman Problem.
% \end{itemize}

% \textbf{Loan Classifaction}
% \begin{itemize}
% 	\item 
% \end{itemize}

\resumesection{Skills and Training}
\begin{itemize}
	\item \textbf{Languages:} Python, SQL, C/++, Ruby Java, C\#, R, Julia, MATLAB, Bash
	\item \textbf{Frameworks/Packages:} Puppet, Docker, Airflow, Kubernetes, SciKit-Learn, TensorFlow, Spark
	\item \textbf{MOOC's:} Python for Data Science, Scientific Programming in Julia, Machine Learning by Andrew Ng
\end{itemize}

\resumesection{Extracurriculars and Awards}
\begin{itemize}
	\item College of Arts \& Sciences Undergraduate Research Award
	\item Delta Sigma Phi Fraternity - Director of Design \& Apparel 
	\item Association for Computing Machinery - Open House Chair 
	\item Mathematical Modelling Seminar
	\item Eagle Scout, Boy Scouts of America, 2014
\end{itemize}


% Don't delete this
\end{document}

